Biodegradable alternatives to plastic mesh bags conventionally used in freshwater

### 2024-02-22 Rdocs/Plots.Rmd
Fixed the clusterfuck that was waterquality data, spaghetti code abounds
now The water quality plots are actually sensible, and thankfully stats remain unchanged.

sqrt transformed Nitrogen and Phosphorous, and now they are normal so I added them to the normal ANOVA group

Also, switched from doing independence test with coin and now im doing kruskal  wallis tests twice, once for site and once for date (not statistically responsible i know, but what choice do we have????)

I am dreading actually writing the manuscript

#water quality time series plots by site
#PARAMS:
  #param(string): a string specifying the water quality parameter
wq_ts_BySite <- function(param){
  #create symbol of parameter name and se for tidy eval in ggplot2 call
  param<- sym(param)
  param_se <- sym(paste(param,"se", sep = "_"))
  ggplot(wq_list$summ_water_quality, aes(x = date, y = !!param)) +
    #geom layers
    geom_jitter(height = 0, size = 2) +
     geom_smooth(method = 'lm', se = T)+
    #labels
    labs(title = paste(param, "Seasonality"), x = "Date")+
    #theme adjustments
    theme_bw() +
    theme_rafa(base_size = 15) +
    scale_color_viridis_d()+
  scale_fill_viridis_d()
}

wq_boxplot_BySite <- function(param){
  #create symbol of parameter name and se for tidy eval in ggplot2 call
  param<- sym(param)
  param_se <- sym(paste(param,"se", sep = "_"))
  ggplot(LPP_FullData, aes(x = site, y = !!param, fill = site)) +
    #geom layers
    geom_boxplot()+
    geom_jitter(width = 0.5, height = 0.0, shape = 21, size = 2) +
    #labels
    labs(title = paste(param, "across sites"), x = "Site")+
    #theme adjustments
    theme_bw() +
    theme_rafa(base_size = 15) +
    scale_fill_viridis_d(option = "E",begin = 0.1, end = 0.9)
}
```

@@

```{r}
ggplot(wq_list$summ_water_quality) +
  #geom_smooth(aes(x = date,color = site, y = NH3), method = "lm", se = T) +
  geom_point(aes(x = date, fill =site, y = NH3), size = 2.5, shape = 21)+

  scale_fill_viridis_d(option = "D") +
  scale_color_viridis_d(option = "D")

ggplot(wq_list$summ_water_quality, aes(x = NH3, y = site, fill = site)) +
  geom_boxplot() +
  geom_jitter(height = 0.2, width = 0.1, shape = 21, size = 1.5) +
  theme_rafa(base_size = 12)+
  facet_wrap(~date) +
  scale_fill_viridis_d() +
  labs(title = "")
```

@@

>>>>

#water quality time series plots by site
#PARAMS:
  #param(string): a string specifying the water quality parameter
wq_ts_BySite <- function(param){
  #create symbol of parameter name and se for tidy eval in ggplot2 call
  param_se <- sym(paste(param,"se", sep = "_"))
  param<- sym(paste(param, "mean", sep = "_"))

  ggplot(water_quality, aes(x = date, y = !!param, color = site)) +
    #geom layers
    geom_errorbar(aes(ymin = !!param - 2*!!param_se, ymax = !!param +2*!!param_se), color = "black") +
    geom_point( size = 2) +
    facet_wrap(~site) +
    #labels
    labs(title = paste(param, "Seasonality"), x = "Date")+
    #theme adjustments
    theme_bw() +
    theme_rafa(base_size = 15) +
    scale_color_viridis_d()+
  scale_fill_viridis_d()
}

wq_boxplot_BySite <- function(param){
  #create symbol of parameter name and se for tidy eval in ggplot2 call

  param_se <- sym(paste(param,"se", sep = "_"))
  param<- sym(paste(param, "mean", sep = "_"))
  ggplot(LPP_FullData, aes(x = site, y = !!param, fill = site)) +
    #geom layers
    geom_boxplot()+
    geom_jitter(width = 0.5, height = 0.0, shape = 21, size = 2) +
    #labels
    labs(title = paste(param, "across sites"), x = "Site")+
    #theme adjustments
    theme_bw() +
    theme_rafa(base_size = 15) +
    scale_fill_viridis_d(option = "E",begin = 0.1, end = 0.9)
}
```

@@

```{r}
ggplot(water_quality, aes( x = sqrt(P_mean))) +geom_histogram(bins = 10)
ggplot(water_quality, aes( x = Nitrogen_mean)) +geom_histogram(bins = 15)
```

@@

```{r}
#prop plots of functional groups
FunGroups_props <- FunGroups %>% 
  select(!FnG_Richness & !fnG_Shannon) %>% 
  pivot_longer(cols = c("collector", "shredder", "scraper", "predator"), names_to = "fn_group", values_to = "counts") %>% 
  group_by(material, date, site) %>% 
  mutate(prop_counts = counts/sum(counts)) %>% 
  group_by(material, fn_group) %>% 
  mutate(avg_prop = mean(prop_counts),
         se_prop = sd(prop_counts)/sqrt(n())) %>% 
  summarise(avg_prop = unique(avg_prop),
            se_prop = unique(se_prop))

ggplot(FunGroups_props, aes(x = material, y = avg_prop, fill = fn_group)) +
  geom_col(position = "dodge") +
  geom_errorbar(aes(ymin = avg_prop -se_prop, ymax = avg_prop +se_prop), position = "dodge") +
  scale_fill_viridis_d(option = "D", begin = 0.2) +
  labs(title = "Distribution of Functional Groups across Bag types",
       y = "Avg. Proportion", caption = "error bars show Standard Error margins")+
  theme_rafa(base_size = 12)
```
